---
title: "Homework 1"
author: Sandra Lu
date: September 2020
output: 
  github_document
---


# Problem 1

**Dataframe with specific requirement**

```{r}
library(tidyverse)
answer_1 = tibble(
  sample_1 = rnorm(10),
  length_1 = sample_1>0,
  vec_char = c("Hello","This","Is","p8105","Data","Science","to","Learn","R","Studio"),
  vec_factor = factor(c("low","medium","high","low","medium","high","low","medium","high","high"))
)
```

**Mean of the dataframe**
```{r}
mean(pull(answer_1, sample_1))
mean(pull(answer_1, length_1))
mean(pull(answer_1, vec_char))
mean(pull(answer_1, vec_factor))
```


**Convert logical, character, and factor variables to numeric variables**

```{r eval=FALSE}
as.numeric(pull(answer_1,length_1)

as.numeric(pull(answer_1,vec_char)
           
as.numeric(pull(answer_1,vec_factor)

```

When converting logical variable to numeric variable, TRUE was converted to 1 while FALSE was converted to 0. It represented the binary nature as we usually code false/true.

Character variables cannot be converted to numeric variable. The results were NA because R cannot recognize the meaning of characters.

When converting factor variable to numeric variable, each level was assigned a number starting from 1. It reflected the categorical meaning of factor variables.

**More conversion**
```{r}
as.numeric(pull(answer_1,length_1))*pull(answer_1,sample_1)

as.factor(pull(answer_1,length_1))*pull(answer_1,sample_1)

as.numeric(as.factor(pull(answer_1,length_1)))*pull(answer_1,sample_1)

```


# Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

**Here is some description of the 'penguins' data set**

A description of all the variables in penguins datasets is as follow 

`r summary(penguins)`.

The size of the dataset is `r nrow(penguins)*ncol(penguins)`.

The mean value of flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm = TRUE)`


**Here is the scatterplot:**

```{r}
ggplot(penguins, aes(x= bill_length_mm, y = flipper_length_mm,color = species)) + geom_point()
```